### 2015-06-15 writing/S'15 LSTM/discussion.tex
LC and partial proofread.
Discussion cleanup.

The results are shown in Figure~\ref{prop-results}. All four models were able to largely memorize the training data (??.?, ??.?, ??.?, and ??.? for $\le$6, pooling across bins). In the $\le$6 setting, the three tree models were able to perform at above ??\% on examples of size $\le$2 with a steady decay in performance continuing through ??.?\% at size 12, and similar, if steeper, decays with smaller training sets. All four robustly beat the simple baselines reported in Bowman et al.: the most frequent class occurs just over 50\% of the time, and a summing model that ignores word order does reasonably on the shortest examples but falls below 60\% by bin 4.

The LSTM performs fairly poorly in the $\le3$ setting, with performance at 3 a mediocre ??.?\%, and an abrupt drop to \% at 4, suggesting that the model did not acquire the needed generalizations. With more ample training data in the $\le6$ condition, though, the LSTM shows fairly good accuracy on short examples, and a smooth decay with no abrupt drop.

>>>>

The results are shown in Figure~\ref{prop-results}. All four models were able to largely memorize the training data, reaching ??.?, ??.?, ??.?, and ??.? overall accuracy for the $\le$6 setting. In that setting, the three tree models were able to perform at above ??.?\% on examples of size $\le$2 with a steady decay in performance continuing through ??.?\% at 12, and similar, if steeper, decays with smaller training sets. The LSTM performs fairly poorly in the $\le3$ setting, with performance at 3 a mediocre ??.?\%, and an abrupt drop to ??.?\% at 4, suggesting that the model did not acquire the needed generalizations. With more ample training data in the $\le6$ condition, though, the LSTM shows fairly good accuracy on short examples, and a smooth decay with no abrupt drop.

All four models robustly beat the simple baselines reported in Bowman et al.: the most frequent class occurs just over 50\% of the time, and a neural bag of words model does reasonably on the shortest examples but falls below 60\% by bin~4.
